%\newpage

\cvsection {\faBook\space Publications}
\textit{\textbf{\colorhref{https://scholar.google.com/citations?user=p89roeEAAAAJ&hl=en&authuser=1}{Google Scholar}:} 270 citations, H-index 5}

\cvsubsection{Peer-reviewed Publications -- Original Research} \vspace{-2mm}

\begin{cvpubs}

\cvpub
{\textbf{JDD Cediel-Becerra}, A Cumsille, S Guerra, Y Ding, Vd Crecy-Lagard, MG Chevrette. ``Targeted genome mining with GATOR-GC maps the evolutionary landscape of biosynthetic diversity.'' 2025. \textit{\textbf{Nucleic Acids Research.}} \textit{\textbf{\colorhref{https://doi.org/10.1093/nar/gkaf606}{10.1093/nar/gkaf606}}}}
{1}

\cvpub
{K Blin, S Shaw, L Vader, J Szenei, ZL Reitz, HE Augustijn, \textbf{JDD Cediel-Becerra}, Vd Crecy-Lagard, RA Koetsier, SE Williams, P Cruz-Morales, S Wongwas, AES Luchsinger, F Biermann, A Korenskaia, MM Zdouc, D Meijer, BR Terlouw, JJJ van der Hooft, N Ziemert, EJN Helfrich, J Masschelein, C Corre, MG Chevrette, GP van Wezel, MH Medema, T Weber. ``antiSMASH 8.0: extended gene cluster detection capabilities and analyses of chemistry, enzymology, and regulation.'' 2025. \textit{\textbf{Nucleic Acids Research.}} \textit{\textbf{\colorhref{https://doi.org/10.1093/nar/gkaf334}{10.1093/nar/gkaf334}}}}
{2}

\cvpub
{MM Zdouc, et al. [398 authors including \textbf{JDD Cediel-Becerra}]. ``MIBiG 4.0: advancing biosynthetic gene cluster curation through global collaboration." 2024. \textit{\textbf{Nucleic Acids Research.}} \textit{\textbf{\colorhref{https://doi.org/10.1093/nar/gkae1115}{10.1093/nar/gkae1115}}}}
{3}

\cvpub
{\textbf{JDD Cediel-Becerra}, JA Suescun Sepulveda, JL Fuentes. ``Prodigiosin Production and Photoprotective/Antigenotoxic Properties in \textit{Serratia marcescens} Indigenous Strains from Eastern Cordillera of Colombia." 2022. \textit{\textbf{Photochemistry and Photobiology.}}\textit{\textbf{\colorhref{https://doi.org/10.1111/php.13507}{10.1111/php.13507}}}}
{4}
\end{cvpubs}

%--------------------------------

\cvsubsection{Peer-reviewed Publications -- Review Articles} \vspace{-2mm}

\begin{cvpubs}

%\cvpub
%{\hspace{-1cm} \textit{First author: ; Total: }}
%{}

\cvpub
{Vd Crecy-Lagard, G Hutinet, \textbf{JDD Cediel-Becerra}, Y Yuan, R Zallot, MG Chevrette, RMMN Ratnayake, M Jaroch, S Quaiyum, S Bruner. ``Biosynthesis and function of 7-deazagu
anine derivatives in bacteria and phages." 2024. \textit{\textbf{Microbiology and Molecular Biology Reviews.}}\textit{\textbf{\colorhref{https://doi.org/10.1128/mmbr.0019923}{10.1128/mmbr.00199-23}}}}
{1}

\end{cvpubs}

%--------------------------------

%\newpage

\cvsubsection{Peer-reviewed Publications -- Book Chapters} \vspace{-2mm}

\begin{cvpubs}

%\cvpub
%{\hspace{-1cm} \textit{First author: ; Total: }}
%{}

\cvpub
{\textbf{JDD Cediel-Becerra}, MG Chevrette. ``Targeted genome mining for natural product discovery." 2025. \textit{\textbf{Methods in Enzymology.}} \textit{\textbf{\colorhref{https://doi.org/10.1016/bs.mie.2025.03.005}{10.1016/bs.mie.2025.03.005}}}}
{1}

\end{cvpubs}

%--------------------------------

%\cvsubsection{Patents} \vspace{-2mm}

%\begin{cvpubs}

%\cvpub
%{\hspace{-1cm} \textit{Total: 2}} % Ref
%{}

%\cvpub
%{. PIPELINE FOR WHAT. XXXXXX. Filed XXXX-XX-XX. \textit{Pending.}}
%{1}

%\end{cvpubs}

%--------------------------------

\cvsubsection{Preprints} \vspace{-2mm}

\begin{cvpubs}

%\cvpub
%{\hspace{-1cm} \textit{Total: 3}} % Ref
%{}

\cvpub
{BR Terlouw, C Huang, D Meijer, \textbf{JDD Cediel-Becerra}, ML Rothe, M Jenner, S Zhow, Y Zhang, CD Fage, Y Tsunematsu, GP van Wezel, SL Robinson, F Alberti, LM Alkhalaf, MG Chevrette, GL Challis, MH Medema. ``PARAS: high-accuracy machine-learning of substrate specificities in nonribosomal peptide synthetases." \textit{bioRxiv. \textbf{\colorhref{https://doi.org/10.1101/2025.01.08.631717}{Preprint available}}}}
{1}


\end{cvpubs}
