%\newpage

\cvsection {\faMicrophone\space Talks \& Abstracts}

\cvsubsection{Invited Talks} \vspace{-2mm}

\begin{cvpubs}

%\cvpub
%{\hspace{-1cm} \textit{Total: }}
%{}

\cvpub
{``GATOR‐GC: Genomic Assessment Tool for Orthologous Regions and Gene Clusters." 10th in the series of John Innes – Rudjer Bošković Summer Schools on Applied Molecular Microbiology. Dubrovnik, Croatia; Sep 12, 2024}
{1}

\end{cvpubs}

%--------------------------------

\cvsubsection{Internal Seminars} \vspace{-2mm}

\begin{cvpubs} 

%\cvpub
%{\hspace{-1cm} \textit{Total: 6}}
%{}

\cvpub
{``Targeted genome mining with GATOR-GC reveals the evolutionary landscape of biosynthetic diversity." Microbiology Seminars, Gainesville, FL. Jan 30, 2025}
{1}

\cvpub
{``PreQ0 gene clusters in \textit{Streptomyces} reveal an anexplored biosynthetic reservoir for drug discovery." Microbiology Seminars, Gainesville, FL. Feb 02, 2024}
{2}

\end{cvpubs}

%--------------------------------

%\newpage
\cvsubsection{Abstracts} \vspace{-2mm}

\begin{cvpubs}

\cvpub
{\textbf{\underline{JDD Cediel-Becerra}},, MG Chevrette, Vd Crecy-Lagard, R Dias. ``Mining 7-Deazapurine Gene Clusters for Novel Secondary Metabolites." Presented at:The American Society of Pharmacognosy (ASP) Annual Meeting. ; Grand Rapids, MI; Aug 05, 2025.}
{1}

\cvpub
{\textbf{\underline{JDD Cediel-Becerra}},, MG Chevrette. ``GATOR-GC Identifies a Rich Landscape of Overlooked Biosynthetic Gene Clusters (BGCs)." Presented at: 10th in the series of John Innes – Rudjer Bošković Summer Schools on Applied Molecular Microbiology. ; Dubrovnik, Croatia; Sep 12, 2024.}
{2}

\cvpub
{M Saldanha, \textbf{\underline{JDD Cediel-Becerra}}, S Manning, F Barona-Gomez, MG Chevrette. ``A global analysis of Bacterial Genomes Links Secondary Metabolism and Antibiotic Resistance." Presented at: Society for Industrial Microbiology and Biotechnology (SIMB) Annual Meeting; Minneapolis, MN; Aug 02, 2024.}
{3}

\cvpub
{\textbf{\underline{JDD Cediel-Becerra}}, A Cumsille, Vd Crecy-Lagard, MG Chevrette. ``Targeted Genomic Searches to Mine Gene Cluster Evolution in Host-Associated Microbes." Presented at: 9th Conference on Beneficial Microbes; Madison, WI; July 21, 2024.}
{4}

\cvpub
{\textbf{\underline{JDD Cediel-Becerra}}, Vd Crecy-Lagard, MG Chevrette. ``GATOR-GC: Genomic Assessment Tool for Orthologous Regions and Gene Clusters ." Presented at: UF Drug Discovery Symposium; Gainesville, FL; April 15, 2024.}
{5}

\cvpub
{M Saldanha, \textbf{\underline{JDD Cediel-Becerra}}, S Manning, MG Chevrette. ``A global analysis of Bacterial Genomes Links Secondary Metabolism and Antibiotic Resistance." Presented at: EPI Research Day; Gainesville, FL; Feb 26, 2024}
{6}

\cvpub
{\textbf{\underline{JDD Cediel-Becerra}}, Vd Crecy-Lagard, MG Chevrette. ``7-Deazapurine-derived natural products: An Incredible Potential Source for Drug Discovery." Presented at: Genetics and Genomics Annual Symposium; Gainesville, FL; Nov 16, 2023.}
{7}

\cvpub
{\textbf{\underline{JDD Cediel-Becerra}}, Vd Crecy-Lagard, MG Chevrette. ``Genome Mining Strategies for Non-Canonical Biosynthetic Gene Clusters." Presented at: Microbiology and Cell Science Annual Symposium; Gainesville, FL; Aug 16, 2023.}
{8}

\cvpub
{MA Gatmaitan, \textbf{\underline{JDD Cediel-Becerra}}, Julia Charske, Mark Ou, Marc G. Chevrette. ``Cockroach-associated Bacteria and Their Antimicrobial Activity." Presented at: American Society of Pharmacognosy (ASP) Annual Meeting; Rockville, MD; Jul 26, 2023}
{9}

\cvpub
{\textbf{\underline{JDD Cediel-Becerra}}, Vd Crecy-Lagard, MG Chevrette. ``Deazaguanine Gene Clusters in \textit{Streptomyces} Reveal Putative Nucleoside-Like Natural Products." Presented at: Society for Industrial Microbiology and Biotechnology (SIMB) Annual Meeting; Minneapolis, MN; Aug 02, 2023.}
{10}

\cvpub
{\textbf{\underline{JDD Cediel-Becerra}}, Vd Crecy-Lagard, MG Chevrette. ``PreQ0 Gene Clusters in \textit{Streptomyces} Reveal an Unexplored Biosynthetic Reservoir." Presented at: American Society of Pharmacognosy (ASP) Annual Meeting; Rockville, MD; Jul 26, 2023.}
{11}

%\end{cvpubs} \begin{cvpubs}

\cvpub
{\textbf{\underline{JDD Cediel-Becerra}}, JA Suescun Sepulveda, JL Fuentes. ``Photoprotective and Antigenotoxic Properties of \textit{Serratia marcescens} Indigenous Strains from Eastern Cordillera of Colombia." Presented at: 19th Congress of the European Society for Photobiology (ESP); WWW and Salzburg, Austria; Aug 30, 2021.}
{12}

\end{cvpubs}
