%\newpage

\cvsection {\faBook\space Publications}

\textit{First author publications: 16; Total publications: 36; Google Scholar Citations: 1885; Google Scholar H-index: 16}

\cvsubsection{Peer-reviewed Publications -- Original Research} \vspace{-2mm}

\begin{cvpubs}

\cvpub
{\hspace{-1cm} \textit{First author: 7; Total: 21}}
{}

\cvpub
{\hspace{-1cm} *\textit{Co-first author, contributed equally}} % Ref
{}

\cvpub
{\textbf{MG Chevrette}, B Himes, C Carlos-Shanley. ``Nutrient availability shifts the biosynthetic potential of soil-derived microbial communities." 2021. \textit{\textbf{Current Microbiology.}} \textit{In press.} \textit{\textbf{\colorhref{https://doi.org/10.1101/2021.09.02.458721}{Preprint available}}}}
{1}

\cvpub
{R Zarnowski, A Noll, \textbf{MG Chevrette}, H Sanchez,R Jones, H Anhalt, J Fossen, A Jaromin, CR Currie, JE Nett, A Mitchell, DR Andes. ``Coordination of fungal biofilm development by extracellular vesicle cargo." 2021. \textit{\textbf{Nature Communications.}} \textit{\textbf{\colorhref{https://doi.org/10.1038/s41467-021-26525-z}{10.1038/s41467-021-26525-z}}}}
{2}

\cvpub
{EJN Helfrich*, R Ueoka*, \textbf{MG Chevrette*}, F Hemmerling, X Lu, S Leopold-Messner, AY Burch, SE Lindow, J Handelsman, J Piel, MH Medema. ``Evolution of combinatorial diversity in \textit{trans}-acyltransferase polyketide synthase assembly lines across bacteria." 2021. \textit{\textbf{Nature Communications.}} \textit{\textbf{\colorhref{https://doi.org/10.1038/s41467-021-21163-x}{10.1038/s41467-021-21163-x}}}}
{3}

\cvpub
{A Hurley, \textbf{MG Chevrette}, DD Acharya, GL Lozano, M Garavito, J Heinritz, L Balderrama, M Beebe, ML DenHartog, K Corinaldi, R Engels, A Gutierrez, O Jona, JHI Putnam, B Rhodes, T Tsang, S Hernandez, C Bascom-Slack, JE Blum, PA Price, D Davis, J Klein, J Pultorak, NL Sullivan, NJ Mouncey, PC Dorrestein, S Miller, NA Broderick, J Handelsman. ``Tiny Earth\: a big idea for STEM education and antibiotic discovery." 2021. \textit{\textbf{mBio.}} \textit{\textbf{\colorhref{https://doi.org/10.1128/mBio.03432-20}{10.1128/mBio.03432-20}}}}
{4}

\cvpub
{MA Schorn*, S Verhoeven*, et al. [104 authors including \textbf{MG Chevrette}]. ``Standardized links between genomic and metabolomic data facilitate integrative mining." 2021. \textit{\textbf{Nature Chemical Biology.}} \textit{\textbf{\colorhref{https://doi.org/10.1038/s41589-020-00724-z}{10.1038/s41589-020-00724-z}}}}
{5}

\cvpub
{HE Ortega*, VB Lourenzon*, \textbf{MG Chevrette*}, LG Ferreira, M Zhao, RFR Alvarenga, WGP Melo, T Venâncio, DR Andes, CR Currie, AD Andricopulo, TS Bugni, MT Pupo. ``Antileishmanial macrolides from ant-associated \textit{Streptomyces} sp. ISID311." 2021. \textit{\textbf{Bioorganic \& Medicinal Chemistry.}} \textbf{\textit{\colorhref{https://doi.org/10.1016/j.bmc.2021.116016}{10.1016/j.bmc.2021.116016}}}}
{6}

\cvpub
{F Zhang, M Zhao, DR Braun, A Audhya, SS Ericksen, JS Piotrowski, J Nelson, J Peng, GE Ananiev, S Chanana, K Barns, J Fossen, \textbf{MG Chevrette}, IA Guzei, C Zhao, L Guo, W Tang, CR Currie, SR Rajski, DR Andes, TS Bugni. ``A marine microbiome antifungal targets urgent-threat drug-resistant fungi." 2020. \textit{\textbf{Science.}} \textbf{\textit{\colorhref{https://doi.org/10.1126/science.abd6919}{10.1126/science.abd6919}}} \linebreak
\textbf{[\textit{\colorhref{https://doi.org/10.1126/science.abf1675}{Highlighted by Science}}]}}
{7}

\cvpub
{Q Wu, K Throckmorton, M Maity, \textbf{MG Chevrette}, DR Braun, SR Rajski, CR Currie, MG Thomas, TS Bugni. ``Bacillibactins E and F from a marine sponge-associated \textit{Bacillus} sp." 2020. \textit{Journal of Natural Products}. \textbf{\textit{\colorhref{https://doi.org/10.1021/acs.jnatprod.0c01170}{10.1021/acs.jnatprod.0c01170}}}}
{8}

\cvpub
{F Zhang, TP Wyche, Y Zhu, DR Braun, J Yan, Y Ge, IA Guzei, \textbf{MG Chevrette}, CR Currie, MG Thomas, SR Rajski, TS Bugni. ``MS-derived isotopic fine structure reveals forazoline A as a thioketone-containing marine-derived natural product." 2020. \textit{\textbf{Organic Letters}}. \textbf{\textit{\colorhref{https://doi.org/10.1021/acs.orglett.9b04535}{10.1021/acs.orglett.9b04535}}}}
{9}

\cvpub
{EJ Caldera*, \textbf{MG Chevrette*}, BR McDonald, CR Currie. ``Local adaptation of bacterial symbionts within a geographic mosaic of antibiotic coevolution." 2019. \textit{\textbf{Applied \& Environmental Microbiology}}. \textbf{\textit{\colorhref{https://doi.org/10.1128/AEM.01580-19}{10.1128/AEM.01580-19}}} \textbf{[\textit{Cover Image for Issue}}]}
{10}

\cvpub
{\textbf{MG Chevrette}, C Carlos-Shanley, KB Louie, BP Bowen, TR Northen, CR Currie. ``Taxonomic and metabolic incongruence in the ancient genus \textit{Streptomyces}." 2019. \textit{\textbf{Frontiers in Microbiology}}. \textbf{\textit{\colorhref{https://doi.org/10.3389/fmicb.2019.02170}{10.3389/fmicb.2019.02170}}}}
{11}

\cvpub
{K Throckmorton*, V Vinnik*, R Chowdhury, TB Cook, \textbf{MG Chevrette}, CD Maranas, BF Pfleger, MG Thomas. ``Directed evolution of an adenylation domain specificity code." 2019. \textit{\textbf{ACS Chemical Biology}}. \textbf{\textit{\colorhref{https://doi.org/10.1021/acschembio.9b00532}{10.1021/acschembio.9b00532}}}}
{12}

\cvpub
{J Yan, \textbf{MG Chevrette}, D Braun, MK Harper, CR Currie, TS Bugni. ``Madurastatin D1 and D2, oxazoline containing siderophores isolated from an \textit{Actinomadura} sp." 2019. \textit{\textbf{Organic Letters}}. \textbf{\textit{\colorhref{https://doi.org/10.1021/acs.orglett.9b02159}{10.1021/acs.orglett.9b02159}}}}
{13}

\cvpub
{\textbf{MG Chevrette}, CM Carlson, HE Ortega, C Thomas, GE Ananiev, KJ Barns, AJ Book, J Cagnazzo, C Carlos, W Flanigan, KJ Grubbs, HA Horn, FM Hoffmann, JL Klassen, JJ Knack, GR Lewin, BR McDonald, L Muller, WGP Melo, AA Pinto-Tom\'{a}s, A Schmitz, E Wendt-Pienkowski, S Wildman, M Zhao, F Zhang, TS Bugni, DR Andes, MT Pupo, CR Currie. ``The antimicrobial potential of \textit{Streptomyces} from insect microbiomes." 2019. \textit{\textbf{Nature Communications}}. \textbf{\textit{\colorhref{https://doi.org/10.1038/s41467-019-08438-0}{10.1038/s41467-019-08438-0}}} \linebreak \textbf{[\textit{\colorhref{https://www.npr.org/sections/health-shots/2019/02/13/694118623/bugs-vs-superbugs-insects-offer-promise-in-fight-against-antibiotic-resistance}{Highlighted by NPR}}]}}
{14}

\cvpub
{RM Stubbendieck, DS May, \textbf{MG Chevrette}, MI Temkin, E Wendt-Pienkowski, J Cagnazzo, CM Carlson, JE Gern, CR Currie. ``Competition among nasal bacteria suggests a role for siderophore-mediated interactions in shaping the human nasal microbiota." 2019. \textit{\textbf{Applied \& Environmental Microbiology}}. \textbf{\textit{\colorhref{https://doi.org/10.1128/AEM.02406-18}{10.1128/AEM.02406-18}}}}
{15}

\cvpub
{N Liu,* H Li,* \textbf{MG Chevrette}, L Zhang, L Cao, H Zhou, X Zhou, Z Zhou, PB Pope, CR Currie, Y Huang, Q Wang. 2019. ``Functional metagenomics reveals polysaccharide-degrading gene clusters and cellobiose utilization pathways in gut microbiota of a wood-feeding termite." \textit{\textbf{ISME Journal}}. \textbf{\textit{\colorhref{https://doi.org/10.1038/s41396-018-0255-1}{10.1038/s41396-018-0255-1}}}}
{16}

\end{cvpubs} \begin{cvpubs}

\cvpub
{N Adnani, \textbf{MG Chevrette}, SN Adibhatla, F Zhang, Q Yu, D Braun, J Nelson, SW Simpkins, BR McDonald, CL Myers, J Piotrowski, C Thompson, CR Currie, L Li, SR Rajski, TS Bugni. ``Co-culture of marine invertebrate-associated bacteria and interdisciplinary technologies enable biosynthesis and discovery of a new antibiotic, keyicin." 2017. \textit{\textbf{ACS Chemical Biology}}.  \textbf{\textit{\colorhref{https://doi.org/10.1021/acschembio.7b00688}{10.1021/acschembio.7b00688}}} \textbf{[\textit{\colorhref{https://www.nature.com/articles/d41586-017-07231-7}{Highlighted by Nature}}]}}
{17}

\cvpub
{AF Sanchez-Larrayoz, NM Elshamy, \textbf{MG Chevrette}, Y Fu, P Giunta, RG Spallanzani, K Ravi, GB Pier, S Lory, T Maira-Litr\'{a}n. ``Complexity of complement-resistance factors expressed by \textit{Acinetobacter baumannii} needed for survival in human serum." 2017. \textit{\textbf{Journal of Immunology}}. \textbf{\textit{\colorhref{https://doi.org/10.4049/jimmunol.1700877}{10.4049/jimmunol.1700877}}}}
{18}

\cvpub
{\textbf{MG Chevrette}, F Aicheler, O Kohlbacher, CR Currie, MH Medema. ``SANDPUMA: Ensemble predictions of nonribosomal peptide chemistry reveals biosynthetic diversity across Actinobacteria." 2017. \textit{\textbf{Bioinformatics}}. \textbf{\textit{\colorhref{https://doi.org/10.1093/bioinformatics/btx400}{10.1093/bioinformatics/btx400}}}}
{19}

\cvpub
{K Blin, T Wolf, \textbf{MG Chevrette}, X Lu, CJ Schwalen, SA Kautsar, HG Suarez Duran, ELC de los Santos, HUK Kim, M Nave, JS Dickschat, DA Mitchell, E Shelest, R Breitling, E Takano, SY Lee, T Weber, MH Medema. ``antiSMASH 4.0 - Improvements in chemistry prediction and gene cluster boundary identification." 2017. \textit{\textbf{Nucleic Acids Research}}. \textbf{\textit{\colorhref{https://doi.org/10.1093/nar/gkx319}{10.1093/nar/gkx319}}}}
{20}

\cvpub
{SS Johnson, \textbf{MG Chevrette}, BL Ehlmann, KC Benison. ``Insights from the metagenome of an acid salt lake: The role of biology in an extreme depositional environment."  2015. \textit{\textbf{PLOS ONE}}. \textbf{\textit{\colorhref{https://doi.org/10.1371/journal.pone.0122869}{10.1371/journal.pone.0122869}}}}
{21}

\end{cvpubs}

%--------------------------------

\cvsubsection{Peer-reviewed Publications -- Review \& Perspective Articles} \vspace{-2mm}

\begin{cvpubs}

\cvpub
{\hspace{-1cm} \textit{First author: 5; Total: 7}}
{}


\cvpub
{\textbf{MG Chevrette}, J Handelsman. ``Needles in haystacks: Reevaluating old paradigms for the discovery of bacterial secondary metabolites." 2021. \textit{\textbf{Natural Product Reports.}} \textbf{\textit{\colorhref{https://doi.org/10.1039/d1np00044f}{10.1039/d1np00044f}}}}
{1}

\cvpub
{\textbf{MG Chevrette*}, A Gavrilidou*, S Mantri*, N Selem-Mojica, N Ziemert, F Barona-G\'{o}mez. ``The confluence of Big Data and evolutionary genome mining for the discovery of natural products." 2021. \textit{\textbf{Natural Product Reports.}} \textbf{\textit{\colorhref{https://doi.org/10.1039/D1NP00013F}{10.1039/D1NP00013F}}}}
{2}

\cvpub
{\textbf{MG Chevrette}, K Guti\'{e}rrez-Garc\'{i}a, N Selem-Mojica, C Aguilar-Mart\'{i}nez, A Ya\~{n}ez-Olvera, HE Ramos-Aboites, PA Hoskisson, F Barona-G\'{o}mez. ``Evolutionary dynamics of natural product biosynthesis in bacteria." 2020. \textit{\textbf{Natural Product Reports}}. \textbf{\textit{\colorhref{https://doi.org/10.1039/c9np00048h}{10.1039/c9np00048h}}}}
{3}

\cvpub
{\textbf{MG Chevrette*}, JR Bratburd*, CR Currie, RM Stubbendieck. ``Experimental microbiomes: models not to scale." 2019. \textit{\textbf{mSystems}}. \textbf{\textit{\colorhref{https://doi.org/10.1128/mSystems.00175-19}{10.1128/mSystems.00175-19}}}}
{4}

\cvpub
{\textbf{MG Chevrette}, CR Currie. ``Emerging evolutionary paradigms in antibiotic discovery." 2019. \textit{\textbf{Journal of Industrial Microbiology \& Biotechnology}}. \textbf{\textit{\colorhref{https://doi.org/10.1007/s10295-018-2085-6}{10.1007/s10295-018-2085-6}}}}
{5}

\cvpub
{IJ Miller, \textbf{MG Chevrette}, JC Kwan. (2017). ``Interpreting microbial biosynthesis in the genomic age: Biological and practical considerations." 2017. \textit{\textbf{Marine Drugs}}. \textbf{\textit{\colorhref{https://doi.org/10.3390/md15060165}{10.3390/md15060165}}} \linebreak \textbf{[\textit{Cover Image for Issue}]}}
{6}

\cvpub
{GR Lewin, C Carlos, \textbf{MG Chevrette}, HA Horn, BR McDonald, RJ Stankey, BG Fox, CR Currie. ``Ecology and evolution of Actinobacteria and their bioenergy applications." 2016. \textit{\textbf{Annual Review of Microbiology}}. \textbf{\textit{\colorhref{https://doi.org/10.1146/annurev-micro-102215-095748}{10.1146/annurev-micro-102215-095748}}}}
{7}

\end{cvpubs}

%--------------------------------

\cvsubsection{Peer-reviewed Publications -- Book Chapters} \vspace{-2mm}

\begin{cvpubs}

\cvpub
{\hspace{-1cm} \textit{First author: 2; Total: 2}}
{}

\cvpub
{\textbf{MG Chevrette}, N Selem-Mojica, C Aguilar, K Labby, ED Bustos-Diaz, J Handelsman, F Barona-G\'{o}mez. ``Evolutionary genome mining for the discovery and engineering of natural product biosynthesis." 2019. \textit{\textbf{Methods in Molecular Biology - Engineering Natural Product Biosynthesis: Methods and Protocols}}. \textit{In press.}}
{1}

\cvpub
{\textbf{MG Chevrette}, PA Hoskisson, F Barona-G\'{o}mez. ``Enzyme evolution in secondary metabolism." 2019. \textit{\textbf{Comprehensive Natural Products III: Chemistry and Biology}}. \textbf{\textit{\colorhref{https://doi.org/10.1016/B978-0-12-409547-2.14712-2}{10.1016/B978-0-12-409547-2.14712-2}}}}
{2}

\end{cvpubs}

%--------------------------------
%\newpage

\cvsubsection{Publications -- Editorial Review Only} \vspace{-2mm}

\begin{cvpubs}

\cvpub
{\hspace{-1cm} \textit{First author: 2; Total: 6}}
{}

\cvpub
{\textbf{MG Chevrette}, J Handelsman. ``From metagenomes to molecules: Innovations in functional metagenomics unlock hidden chemistry in the human microbiome." 2020. \textit{\textbf{Biochemistry}}. \textbf{\textit{\colorhref{https://doi.org/10.1021/acs.biochem.0c00033}{10.1021/acs.biochem.0c00033}}}}
{1}

\cvpub
{\textbf{MG Chevrette}. ``Natural products reawakened: New trends in discovery and development." 2018. \textit{\textbf{SIMB News Magazine}, Society for Industrial Microbiology and Biotechnology}. }
{2}

\cvpub
{DR Braun, \textbf{MG Chevrette}, D Acharya, CR Currie, SR Rajski, TS Bugni. ``Draft genome of \textit{Micromonospora sp. WMMA1996}, a marine sponge-associated bacterium." 2018. \textit{\textbf{Genome Announcements}}. \textbf{\textit{\colorhref{https://doi.org/10.1128/genomeA.00077-18}{10.1128/genomeA.00077-18}}}}
{3}

\cvpub
{DR Braun, \textbf{MG Chevrette}, D Acharya, CR Currie, SR Rajski, K Ritchie, TS Bugni. ``Complete genome of \textit{Dietzia sp. WMMA184}, a marine coral-associated bacterium." 2018. \textit{\textbf{Genome Announcements}}. \textbf{\textit{\colorhref{https://doi.org/10.1128/genomeA.01582-17}{10.1128/genomeA.01582-17}}}}
{4}

\cvpub
{N Adnani, DR Braun, BR McDonald, \textbf{MG Chevrette}, CR Currie, TS Bugni. ``Draft genome of \textit{Micromonospora sp. WMMB-235}, a marine ascidian-associated bacterium." 2017. \textit{\textbf{Genome Announcements}}. \textbf{\textit{\colorhref{https://doi.org/10.1128/genomeA.01369-16}{10.1128/genomeA.01369-16}}}}
{5}

\end{cvpubs} \begin{cvpubs}

\cvpub
{N Adnani, DR Braun, BR McDonald, \textbf{MG Chevrette}, CR Currie, TS Bugni. ``Complete genome sequence of \textit{Rhodococcus sp. strain WMMA185}, a marine sponge-associated bacterium." 2016. \textit{\textbf{Genome Announcements}}. \textbf{\textit{\colorhref{https://doi.org/10.1128/genomeA.01406-16}{10.1128/genomeA.01406-16}}}}
{6}

\end{cvpubs}

%--------------------------------

\cvsubsection{Patents} \vspace{-2mm}

\begin{cvpubs}

\cvpub
{\hspace{-1cm} \textit{Total: 1}} % Ref
{}

\cvpub
{DC Gray, E Li, BR Bowman, GL Verdine, K Robison, \textbf{MG Chevrette}, D Udwary, PS Wang, A Li, JP Morgenstern. Compositions and methods for the production of compounds. Priority 2016-10-28, filed 2017-10-27, published 2019-08-29. \textbf{\textit{\colorhref{https://patents.google.com/patent/US20190264184A1/en}{US20190264184A1}}}}
{1}

\end{cvpubs}

%--------------------------------

\cvsubsection{Preprints, Submitted, \& Under Review} \vspace{-2mm}

\begin{cvpubs}

\cvpub
{\hspace{-1cm} \textit{Total: 6}} % Ref
{}

\cvpub
{BR McDonald, \textbf{MG Chevrette}, JL Klassen, HA Horn, EJ Caldera, E Wendt-Pienkowski, MJ Cafaro, AC Ruzzini, EB Van Arnam, GM Weinstock, NM Gerardo, M Poulsen, G Suen, J Clardy, CR Currie. ``Biogeography and microscale diversity shape the biosynthetic potential of fungus-growing ant-associated \textit{Pseudonocardia}." \textit{In revision. \textbf{\colorhref{https://doi.org/10.1101/545640}{Preprint available}}}}
{1}

\cvpub
{J Yan, Q Wu, EJN Helfrich, \textbf{MG Chevrette}, DR Braun, H Heyman,  GE Ananiev, SR Rajski, CR Currie, J Clardy, TS Bugni. ``Bacillimidazoles A−F, imidazolium-containing antibacterial compounds isolated from a marine \textit{Bacillus}." \textit{In revision.}}
{2}

\cvpub
{BD Lee, A Gitter, CS Greene, S Raschka, F Maguire, AJ Titus, MD Kessler, AJ Lee, \textbf{MG Chevrette}, PA Stewart, T Britto-Borges, EM Cofer, KH Yu, JJ Carmona, EJ Fertig, AA Kalinin, B Signal, BJ Lengerich, TJ Triche Jr, SM Boca. ``Ten quick tips for deep learning in biology." \textit{Under review. \textbf{\colorhref{https://arxiv.org/abs/2105.14372}{Preprint available}}}}
{3}

\cvpub
{GR Lewin, NM Davis, BR McDonald, AJ Book, \textbf{MG Chevrette}, S Suh, A Boll, CR Currie. ``Long-term cellulose enrichment selects for highly cellulolytic consortia and competition for public goods." \textit{Submitted. \textbf{\colorhref{https://doi.org/10.1101/2020.09.18.304485}{Preprint available}}}}
{4}

\cvpub
{Q Wu, JX Yan, \textbf{MG Chevrette}, S Chanana, BA Bell, M Maity, DR Braun, IA Guzei, MG Thomas, SR Rajski, TS Bugni. ``Ecteinamines A and B: new nonribosomal peptides with an unprecedented skeleton from marine bacterium \textit{Micromonospora} sp." \textit{Submitted.}}
{5}

\cvpub
{K Gotting, DS May, J Sosa-Calvo, L Khadempour, CB Francouer, AB Lopez, MW Thairu, S Sandstrom, CM Carlson, \textbf{MG Chevrette}, A Rodriques, MT Pupo, TS Bugni, TR Schultz, JS Johnston, NM Gerardo, CR Currie. ``Genomic diversification of the specialized parasite of the fungus-growing ant symbiosis." \textit{Submitted.}}
{6}

\end{cvpubs}